\huge The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-06-23 Writeup/kohler_clarke_2021.tex
credit David Wade

\begin{figure}[hptb]
\centering
\includegraphics[width=0.75\linewidth]{../figures/figure1.pdf}
\caption{Subgroup relationships with indices 2 (solid lines) and 3 (dashed line) are shown in (A). All other relationships can be inferred by identifying the shortest path through the hierarchy, and multiplying the subgroup indices. For example, \textit{P1} is related to \textit{P6} through \textit{P6}\textrightarrow\textit{P3} (index 2) and \textit{P3}\textrightarrow\textit{P1} (index 3) so \textit{P1} is also a subgroup of \textit{P6} with index $3 \times 2 = 6$. We also show enlarged versions of some of the subgroup relationships involving \textit{P6} (B, shown in red) and \textit{PMM} (C, shown in blue) and highlight the symmetries within the subgroups to emphasize how the supergroup can be generated by adding additional transformations to the subgroup.}
\label{fig:subgroups}
\end{figure}

>>>>

\begin{figure}[hptb]
\centering
\includegraphics[width=0.75\linewidth]{../figures/figure1.pdf}
\caption{Subgroup relationships with indices 2 (solid lines) and 3 (dashed line) are shown in (A). All other relationships can be inferred by identifying the shortest path through the hierarchy, and multiplying the subgroup indices. For example, \textit{P1} is related to \textit{P6} through \textit{P6}\textrightarrow\textit{P3} (index 2) and \textit{P3}\textrightarrow\textit{P1} (index 3) so \textit{P1} is also a subgroup of \textit{P6} with index $3 \times 2 = 6$. We also show enlarged versions of some of the subgroup relationships involving \textit{P6} (B, shown in red) and \textit{PMM} (C, shown in blue) and highlight the symmetries within the subgroups to emphasize how the supergroup can be generated by adding additional transformations to the subgroup. Illustration adapted from \citet{wade_crystal_1993}.}
\label{fig:subgroups}
\end{figure}
